A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-10-05 paper/journal.tex
Final version

\title[Drawings of Graphs with High Crossing Resolution]{A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution%
\thanks{A preliminary version of this work has appeared in the Proceedings of the 26th International Symposium on Graph Drawing and Network Visualization (GD 2018).
This work is supported by the DFG grant Ka812/17-1}}

@@

\paragraph{Acknowledgments.} The authors would also like to thank Simon Wegendt and Jessica Wolz for implementing the first version of our prototype.

>>>>

\title[Drawings of Graphs with High Crossing Resolution]{A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution}

@@

\paragraph{Acknowledgments.} The authors would like to thank Simon Wegendt and Jessica Wolz for implementing the first version of our prototype. This work is supported by the DFG grant Ka812/17-1. A preliminary version of this work has appeared in the Proceedings of the 26th International Symposium on Graph Drawing and Network Visualization (GD 2018).
